### 2019-10-17 manuscript/manuscript.rmd
update rdata, reknitr'd with all new analyses working (I think)
another pass at taxon_rectangles figure

---
csl: plos.csl
output:
  pdf_document: default
  github_document: default
  html_document: default
bibliography: manuscript.bib
---

@@

taxon_rectangles = lapply(
	sequence_matrices,
	function ( sequence_matrix ){
		clade_rects(sequence_matrix)
	}
) %>%
bind_rows()

clade_colors = viridis( length(clades) )
names( clade_colors ) = clades

ggplot(data=taxon_rectangles) + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) + 
	# scale_fill_manual(guide = guide_legend(reverse=TRUE))
	# scale_fill_manual(values = clade_colors, guide = guide_legend(reverse=TRUE))
	scale_fill_discrete(guide = guide_legend(reverse=TRUE)) +
	facet_wrap( ~ manuscript_matrix )

>>>>

---
csl: plos.csl
output:
  github_document: default
  pdf_document: default
  html_document: default
bibliography: manuscript.bib
---

@@

taxon_rectangles = lapply(
	sequence_matrices,
	function ( sequence_matrix ){
		clade_rects(sequence_matrix)
	  }
  ) %>%
  bind_rows() %>%
  filter(!grepl('only', matrix)) %>%
  mutate(matrix = str_replace_all(matrix, "_", " "))  %>%
  arrange(year, matrix)

ggplot(data=taxon_rectangles) + 
	scale_x_continuous(name="Genes Sampled") + 
	scale_y_continuous(name="Taxa Sampled") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) + 
	scale_fill_brewer(type="qual", direction=-1, palette="Set3", guide = guide_legend(reverse=TRUE)) +
	facet_wrap( ~ matrix, labeller = label_wrap_gen(width = 18, multi_line = TRUE)) + 
  theme_void() +
  theme(
    strip.background = element_rect(fill = "lightgrey"),
    strip.text.x = element_text(size = 8),
    panel.background = element_rect(fill ="#f9f9f9"),
    # panel.grid.major = element_blank(),
    # panel.grid.minor = element_blank()
  )
